The impact of forest management on the temperature sensitivity of organic matter turnover

### 2024-08-23 Manuscript_draft/Draft.Rmd
Minor commit after ouor talk, syncing just in case

# Introduction
The soil is one of the largest terrestrial reservoirs of carbon, containing approximately three times more carbon than the atmosphere or the vegetation on Earth (IPCC, 2021). Soil carbon is released to the atmosphere as carbon dioxide (CO₂) through decomposition of organic matter by microbes (heterotrophic respiration) and root respiration (autotrophic respiration). This process, i.e., soil respiration, constitutes the main carbon efflux into the atmosphere (ref). Under the new climate change scenarios increases of Co2 efflux from soils are expected (Schlesinger and Andrews, 2000), in turn this can imply a positive feedback to future warming (ref). Because soil respiration is highly sensitive to soil temperature and soil moisture (ref), understanding the responses of soil respiration to these microclimatic conditions, which are affected by global change factors as climate change and forest management is critical for predicting future atmospheric CO2 concentrations.

>>>>

# Introduction
The soil is one of the largest terrestrial reservoirs of carbon, containing approximately three times more carbon than the atmosphere or the vegetation on Earth (IPCC, 2021). Soil carbon is released to the atmosphere as carbon dioxide (CO₂) through decomposition of organic matter by microbes (heterotrophic respiration) and root respiration (autotrophic respiration). This process, i.e., soil respiration, constitutes the main carbon efflux into the atmosphere (ref). Under the new climate change scenarios increases of CO₂ efflux from soils are expected (Schlesinger and Andrews, 2000), in turn this can imply a positive feedback to future warming (ref). Because soil respiration is highly sensitive to soil temperature and soil moisture (ref), understanding the responses of soil respiration to these microclimatic conditions, which are affected by global change factors as climate change and forest management is critical for predicting future atmospheric CO2 concentrations.
